---
title: "hw1"
output: pdf_document
---
## Homework #1

### Exercise 3.1
Using the famous Galton data set from the mosaicData package:

```{r}
library(mosaic)
head(Galton, n=5)
```
```{r}
summary(Galton)
```

```{r}
?Galton
```
#### 1. Create a scatterplot of each person's height against their father's height
```{r}
ggplot(data = Galton, aes(x = father, y = height)) + geom_point(colour="purple") + xlab("Father's Height") + ylab("Height")
```

#### 2. Separate your plot into facets by sex

```{r}
ggplot(data = Galton, aes(x = father, y = height)) + geom_point(colour="purple") + xlab("Father's Height") + ylab("Height") + facet_wrap(~sex)
```

#### 3. Add regression lines to all of your facets
```{r}
ggplot(data = Galton, aes(x = father, y = height)) + geom_point(colour="purple") + xlab("Father's Height") + ylab("Height") + facet_wrap(~sex) + geom_smooth(method="lm", colour="green")
```

### Exercise 3.2
Using the RailTrail data set from the mosaicData package:

```{r}
head(RailTrail, n=5)
```

```{r}
summary(RailTrail)
```
```{r}
?RailTrail
```
#### 1. Create a scatterplot of the number of crossings per day volume against the high temperature that day

```{r}
ggplot(data = RailTrail, aes(x = volume, y = hightemp)) + geom_point(colour="purple") + xlab("Volume") + ylab("High Temperature (F)")
```

#### 2. Separate your plot into facets by weekday

```{r}
ggplot(data = RailTrail, aes(x = volume, y = hightemp)) + geom_point(colour="purple") + xlab("Volume") + ylab("High Temperature (F)") + facet_wrap(~weekday)
```

#### 3. Add regression lines to the two facets

```{r}
ggplot(data = RailTrail, aes(x = volume, y = hightemp)) + geom_point(colour="purple") + xlab("Volume") + ylab("High Temperature (F)") + facet_wrap(~weekday) + geom_smooth(method="lm", colour="green")
```

### Exercise 3.3
Angelica Schuyler Church (1756-1814) was the daughter of New York Governer Philip Schuyler and sister of Elizabeth Schuyler Hamilton. Angelica, New York was named after her. Generate a plot of the reported proportion of babies born with the name Angelica over time and interpret the figure.

```{r}
library(babynames) 
head(babynames, n=5)
```

```{r}
summary(babynames)
```

```{r}
?babynames
```

```{r}
library(tidyr)
library(magrittr)
ggplot(data = babynames %>%
filter(name=="Angelica"), aes(x = year, y = prop)) +
geom_line() + xlab("Year") + ylab("Proportion") +
ggtitle("Proportion of Angelicas") + theme(plot.title = element_text(hjust=0.5))
```

### Exercise 3.4
The following questions use the Marriage data set from the mosaicData package.

```{r}
head(Marriage, n = 5)
```

```{r}
summary(Marriage)
```

```{r}
?Marriage
```

#### 1. Create an informative and meaningful data graphic.

```{r}
ggplot(data = Marriage, aes(x = age)) + facet_wrap(~race) + geom_histogram(binwidth = 10, colour="purple") + ggtitle("Marriage Records By Race") + theme(plot.title = element_text(hjust=0.5))
```

#### 2. Identify each of the visual cues that you are using, and describe how they are related to each variable.

* Position: Title in the center (horizontally). Each facet is grouped by race
* Length: Age (x axis) ranges from 16.27 to 74.25. Min count (y axis) is 1 (hispanic) and max count is 74 (white).
* Direction: For american Indian and hispanic there isn't a clear trend (not enough data) but for white and black the count decreases as the person ages. 
* Color: outlining purple

#### 3. Create a data graphic with at least five variables (either quantitative or categorical). For the purposes of this exercise, do not worry about making your visualization meaningful|just try to encode five variables into one plot.

```{r}
g1 <-Marriage %>% mutate(col_bool = ifelse(college == 0 | is.na(college), FALSE, TRUE))

ggplot(data = Marriage %>% mutate(group = paste(race,sign,g1, sep="-")), aes(x = age, y=count(appdate), z = group)) + geom_point() + facet_wrap(~race)

```

Here I'm using
1. race
2. college 
3. age
4. sign
5. appdate
