---
title: "hw4"
output: pdf_document
---

### Exercise 4.13
Name every player in baseball history who has accumulated at least 300 home runs (HR)
and at least 300 stolen bases (SB).
```{r}
library(dplyr)
library(Lahman)
str(Batting)
str(Master)
str(Teams)
```

```{r}
x<-Batting %>% group_by(playerID) %>%summarize(NHR=sum(HR), NSB=sum(SB)) %>% filter(NHR >= 300 & NSB>=300) %>% select(playerID) %>% left_join(Master, by = c("playerID"="playerID")) %>% select(nameGiven)%>% arrange(nameGiven)
x
```

### Exercise 4.14
Name every pitcher in baseball history who has accumulated at least 300 wins (W) and
at least 3,000 strikeouts (SO).

```{r}
x<-Batting %>% group_by(playerID, teamID) %>% summarize(NSO=sum(SO)) %>% select(playerID, teamID, NSO)
y<-Teams %>% group_by(teamID) %>% summarize(NW=sum(W)) %>% filter(NW >= 300) %>% select(teamID, NW)
z<-x %>% left_join(y, by = c("teamID"="teamID")) %>% group_by(playerID) %>% summarize(NNSO=sum(NSO), NNW=sum(NW)) %>% filter(NNSO>=2500) %>% select(playerID, NNW, NNSO) %>% left_join(Master, by = c("playerID"="playerID")) %>% select(nameGiven)%>% arrange(nameGiven)
z
```
### Exercise 4.15
Identify the name and year of every player who has hit at least 50 home runs in a single
season. Which player had the lowest batting average in that season?

```{r}
players_50_hr <- Batting %>% group_by(playerID, yearID) %>% summarize(NHR=sum(HR)) %>% filter(NHR>=50) %>% select(playerID, yearID) %>% left_join(Master, by = c("playerID"="playerID")) %>% select(nameGiven, yearID) %>% arrange(nameGiven, yearID)
players_50_hr
```
